Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-31 draft/paper1_jenny.tex
Edit color_ell 2

%% ------------------------------------------------------------------------------------ %% 
	Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
	band image and the flux-weighted isophotal shape, while more useful information 
	can be gathered from the HSC images of these massive galaxies.
	The ellipticity and $k$-corrected optical color profiles are particularly 
	interesting.
	We extract ellipticity profile using \texttt{Ellipse} by setting the shape of each 
	isophote free. 
	And by applying the $i$-band isophotes to images of other bands in the 
	forced-photometry way, we can also measure the color profiles too. 
	We apply Galactic extinction correction and \texttt{iSEDFit} $k$-correction to 
	both the $g-r$ and $g-i$ color profiles.
	The PSF smearing effect will make the central isophotal shape rounder than the 
	real value, while the seeing differences between filters will bias the central 
	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
	will become redder when the seeing effect is not corrected.}. 
	At the same time, it is more difficult to extract reliable ellipticity and 
	color profiles out to 100 kpc: at low surface brightness region, isophotal shape 
	becomes unstable and easily affected by any contamination; the color profile in
	the outskirt also becomes very sensitive to background level and noise level in 
	either band. 
	In this work, we will only

   These quantities contain interesting information about the physical processes that 
    shape galaxies. We also want to be sure that we do not introduce any systematic bias in 
    our mass determinations because of systematic changes in color profile with stellar or 
    halo mass.

    %\begin{enumerate}
    %    
    %    \item To see whether the ellipticity profile depends strongly on environment, 
    %        and to see whether or not the fact that we use an using average isophotal 
    %        shape for our our 1-D \mden{} profiles has any impact on our results.
    %    
    %    \item To verify that the average color gradient does not depend strongly on 
    %        the environment and that is not steep enough to cause a problem with our 
    %        choice the assumption that it is reasonable to use average \m2l for 
    %        comparing massive galaxies. 
    %        We extract color profiles by applying the isophotes in $i$-band to images 
    %        in other bands in ``forced photometry'' manner.  
    %        
    %\end{enumerate}

    We compute ellipticities and color profiles in the radial range of 5-50 kpc 
    (this is the range where we can safely ignore differences in sky subtraction and 
    seeing across different bands).

@@

    We find that in general, the ellipticities of massive galaxies increases with 
    radius from $e\le 0.2$ around 5-10 kpc to $e{\sim} 0.3$ at 40-50 kpc. 
    This is consistent with previous 2-D modeling results from \citet{Huang2013a}. 
    The ellipticity profiles of the \mtot{}-matched samples are very similar at 
    $r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
    However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
    ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
    profiles are very similar.  
    This further hints that massive central galaxies in different halos but with 
    similar ``in-situ'' mass may experience different late-time merging histories. 
    Overall, the relative low ellipticity value and the fact that the ellipticity 
    gradients are shallow lead us to conclude that the use of an average 
    isophotal ellipticity is fine for this present study.

    Previous attempts to constrain ellipticity gradients have relied on image 
    stacking techniques (e.g. \citealt{Tal2011}, \citealt{DSouza2015}). 
    Compared to our measurements, we find that stacked ellipticity profiles tend to 
    underestimate the ellipticity in the outskirt. 
    Ellipticity profiles contain additional information about the assembly histories 
    and in future work, it would be of interest to compare our ellipticity profiles 
    with predictions from hydrodynamic simulations such as Illustris 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
    (\citealt{Dubois2014}).

>>>>

%% ------------------------------------------------------------------------------------ %% 
	Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
	band image and the flux-weighted isophotal shape, while more useful information 
	can be gathered from the HSC images of these massive galaxies.
	The ellipticity and $k$-corrected optical color profiles are particularly 
	interesting.
	We extract ellipticity profile using \texttt{Ellipse} by setting the shape of each 
	isophote free. 
	And by applying the $i$-band isophotes to images of other bands in the 
	forced-photometry way, we can also measure the color profiles too. 
	We apply Galactic extinction correction and \texttt{iSEDFit} $k$-correction to 
	both the $g-r$ and $g-i$ color profiles.
	The PSF smearing effect will make the central isophotal shape rounder than the 
	real value, while the seeing differences between filters will bias the central 
	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
	will become redder when the seeing effect is not corrected.}. 
	At the same time, it is more difficult to extract reliable ellipticity and 
	color profiles out to 100 kpc: at low surface brightness region, isophotal shape 
	becomes unstable and easily affected by any contamination; the color profile in
	the outskirt also becomes very sensitive to background level and noise level in 
	either band. 
	In this work, we will focus on the median ellipticity and color profiles between 
	8--60 kpc where we can safely ignore the above issues.

	The ellipticity of the isophote contains information about the 3-D geometry 
	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematic (e.g. 
	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
	Left of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC massive 
	galaxies and highlight the median profiles for the same three \mtot{} bins used 
	in Fig \ref{fig:avg_prof}. 
	In general, the ellipticity of massive galaxy slowly increases with radius.
	One can even notice this trend by directly comparing the shape of galaxy between 
	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
	($< 0.2$); but more massive galaxies become increasingly more elongated in their
	stellar halo. 	
	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
	$e{\sim} 0.4$ at 50-60 kpc.
	This is consistent with previous 2-D modeling results from \citet{Huang2013a}.
	If accreted stars dominate the stellar halos of massive galaxies, this 
	mass-dependent ellipticity profile may lead us to some insights about the 
	differences in their assembly history (e.g. average time since last merger, 
	average merger mass ratio).
	We also compare our ellipticity profiles with previous ones that are based on 
	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
	the concentration galaxies with $11.0<$\logms{}$<11.4$ from 
	\citealt{DSouza2015}), 
	We notice that the stacked image sometimes fails to recover the ellipticity 
	profile, probably due to the uncertainties in aligning galaxies before the 
	stacking process.

@@

    % TODO: Move this to Paper II 
    %The ellipticity profiles of the \mtot{}-matched samples are very similar at 
    %$r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
    %However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
    %ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
    %profiles are very similar.  
    %This further hints that massive central galaxies in different halos but with 
    %similar ``in-situ'' mass may experience different late-time merging histories. 
    %Overall, the relative low ellipticity value and the fact that the ellipticity 
    %gradients are shallow lead us to conclude that the use of an average 
    %isophotal ellipticity is fine for this present study.

    Ellipticity profiles contain additional information about the assembly histories 
    and in future work, it would be of interest to compare our ellipticity profiles 
    with predictions from hydrodynamic simulations such as Illustris 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
    (\citealt{Dubois2014}).
